---
title: "Treatment Plan Comparison"
subtitle: 'Take Home Challenge'
author: "Apostrophe/Raja Jain"
date: "5/24/2021"
output:
  ioslides_presentation: default
  slidy_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
Sys.setenv(RETICULATE_PYTHON = "/Users/raja_/Documents/GitHub/apostrophe/venv/bin/python")
library("reticulate")
library(ggplot2)
library(dplyr)
library(MASS)
library(glmnet)
library(mlbench)
library(survival)
library(survminer)
library(tidyverse)
library(lmtest)
library(lawstat)
library(nortest)
library(rstatix)
library(knitr)
library(ggpubr)
library(MASS)
library(bestglm)
library(leaps)
library(sjlabelled)
library(caret)
library(mltools)
library(scales)
library(polycor)

py_install("pandas", envname = "venv")

source_python("read_pickle.py")

ab_test_data = read_pickle_file("ab_test_collection_df.pkl")
target_treatment_group_data = read_pickle_file("target_treatment_group_data.pkl")

ab_test_data$treatment_plan.group = unlist(ab_test_data$treatment_plan.group)
par(mar=c(5,5,0,0))
```

## Goal
- Explore the AB Test dateset and determine if the treatment group is correlated with shifts across other tracked items

## AB Test Data Overview
- Dates of Collection:
  - 2021-01-28 to 2021-04-12 
- ~20,000 records


```{r, fig.width=5, fig.height=5, echo=FALSE}
treatment_groups_all_data = ab_test_data %>% count(treatment_plan.group)
treatment_groups_all_data$percent =  round(100*treatment_groups_all_data$n/sum(treatment_groups_all_data$n), 1)

pie(
  treatment_groups_all_data$n,
  labels = paste(treatment_groups_all_data$treatment_plan.group, sep = " ",
                 treatment_groups_all_data$percent, "%"), 
  main = "Treatment Plans by Percentage"
)
```

## Feature Engineering
- Created columns to measure time between campaign creation and several other time measures
- Created **PURCHASED** column
  - marked TRUE if a `purchase_date` was present for a given record  
  
<br>

```{r}
target_columns = c(
  "treatment_plan.group",
  "treatment_plan.time_between_campaign_start_and_consultation_completed",
  "treatment_plan.time_between_campaign_start_and_viewed_treatment_plan",
  "treatment_plan.time_between_campaign_start_and_viewed_checkout_page",
  "treatment_plan.time_between_campaign_start_and_purchase_date",
  "PURCHASED"  
)

target_treatment_group_data = target_treatment_group_data[, target_columns]

target_treatment_group_data$treatment_plan.group = as_factor(target_treatment_group_data$treatment_plan.group)


treatment_purchased_summary = target_treatment_group_data %>% 
  count(treatment_plan.group, PURCHASED) %>%
  group_by(treatment_plan.group) %>%
  mutate(prop = prop.table(n))

ggplot(treatment_purchased_summary, aes(fill=PURCHASED, y=n, x=treatment_plan.group)) + 
  geom_bar(position="stack", stat="identity") + 
  theme_pubclean() +
  ggtitle("Count PURCHASED by Treatment Plan") +
  xlab("")


treatment_purchased_summary = treatment_purchased_summary %>% 
  mutate(prop=scales::percent(prop))

kable(treatment_purchased_summary)
```

## Compute Correlation between
- Treatment Plan and
- PURCHASED

```{r}
polychor(
  target_treatment_group_data$treatment_plan.group,
  target_treatment_group_data$PURCHASED,
  ML=T
)
```

## Reverse Engineering Relations Between Treatment Plans and Times

```{r}
target_treatment_group_data_2 = subset(target_treatment_group_data, select = -c(PURCHASED))

full_model = glm(
  treatment_plan.group ~ .,
  data = target_treatment_group_data_2,
  family='binomial'
)

summary(full_model)
plot(full_model)
```

## Compute Correlation between 
- Treatment Plan
- Time between Campaign Start and When the Treatment Plan was Viewed

```{r}

poly_serial_results = polyserial(
  target_treatment_group_data$treatment_plan.time_between_campaign_start_and_viewed_treatment_plan,
  target_treatment_group_data$treatment_plan.group,
  std.err = T
)

poly_serial_results$cuts
 
```


